### GLS positional data

#### Prepare workspace & load data
```{r, fake_loc_setup, echo=TRUE, eval = FALSE, message=FALSE}
# Load libraries
library(arrow) # for loading parquet files
library(dplyr) # for easily working with data
library(lubridate) # for some enhanced date functionality
library(ggplot2) # for plotting
library(sf) # for GIS work
library(maps)

# deactivate spherical geometry (s2) for sf
sf::sf_use_s2(FALSE)

# point R to the folder where the data is, e.g.
data_dir <- "path/where/you/unzipped/files/data"
```

```{r, loc_setup, echo=FALSE, message=FALSE}
# THE ABOVE BLOCK IS FAKE TO SHOW HOW TO SET THE PATH
# Load libraries
library(arrow) # for loading parquet files
library(dplyr) # for easily working with data
library(lubridate) # for some enhanced date functionality
library(ggplot2) # for plotting
library(sf) # for GIS work
library(maps)

# deactivate spherical geometry (s2) for sf
sf::sf_use_s2(FALSE)
```

```{r, generate_loc_path, echo = FALSE, message = FALSE}
load_chunk <- knitr::knit_expand(text = c(
    "```{r, load_loc_files}",
    'myirmalocs <- read_parquet(file.path(data_dir, "{{IRMA_pos_path}}"))',
    "```"))

```

`r knitr::knit(text=load_chunk)`

#### Explore data

Some examples on how to quickly explore your IRMA positional data.

```{r, loc_explore,  echo=TRUE, message=TRUE}
myirmalocs %>%
    dplyr::group_by(colony, year_tracked, age_deployment) %>%
    dplyr::summarise(n_birds_tracked = n_distinct(individ_id))
```

```{r, loc_explore,  echo=TRUE, message=TRUE}
myirmalocs %>%
    dplyr::group_by(colony, year_tracked, loc_type) %>%
    dplyr::summarise(n_positions = n_distinct(id))
```

#### Make a map

Some examples on how to quickly map your IRMA positional data.

```{r, plot_loc, echo = TRUE, message = TRUE}
myirmalocs %>%
    dplyr::mutate(year = year(date_time)) %>%
    sf::st_as_sf(coords = c("lon", "lat"), crs = 4326) ->
myirmalocs

worldmap <- ggplot2::map_data("world")

ggplot() +
    geom_polygon(data = worldmap, aes(x = long, y = lat, group = group)) +
    geom_sf(data = myirmalocs, aes(colour = loc_type), size = .1) +
    coord_sf(
        lims_method = "geometry_bbox"
    ) +
    theme_light() +
    theme(legend.position = "bottom")
```

