### Immersion data

#### Prepare workspace & load data
```{r, fake_imm_setup, echo=TRUE, eval = FALSE, message=FALSE}
# Load libraries
library(arrow) # for loading parquet files
library(dplyr) # for easily working with data
library(lubridate) # for some enhanced date functionality
library(ggplot2) # for plotting

# point R to the folder where the data is, e.g.
data_dir <- "path/where/you/unzipped/files/data"
```

```{r, imm_setup, echo=FALSE, message=FALSE}
# THE ABOVE BLOCK IS FAKE TO SHOW HOW TO SET THE PATH
# Load libraries
library(arrow) # for loading parquet files
library(dplyr) # for easily working with data
library(lubridate) # for some enhanced date functionality
library(ggplot2) # for plotting
```

```{r, generate_imm_path, echo = FALSE, message = FALSE}
load_chunk <- knitr::knit_expand(text = c(
    "```{r, load_imm_files}",
    'immersion <- read_parquet(file.path(data_dir, "{{imm_path}}"))',
    "```"))

```

`r knitr::knit(text=load_chunk)`

#### Explore data

Some examples on how to quickly explore your immersion data.

```{r, imm_explore, echo = TRUE, message = TRUE}
immersion %>%
    dplyr::mutate(year = year(date_time)) %>%
    dplyr::group_by(year) %>%
    dplyr::summarise(n_birds_tracked = n_distinct(individ_id))
```

#### Make a plot

An example of plotting immersion data.
```{r, plot_imm, echo = TRUE, message = TRUE}
one_individ <- immersion[immersion$individ_id %in% unique(immersion$individ_id)[1], ]
one_year <- one_individ[year(one_individ$date_time) %in% unique(year(one_individ$date_time))[1], ]
one_year$doy <- strftime(one_year$date_time, format = "%j")
one_year <- aggregate(std_conductivity ~ doy, one_year, mean)
plot(one_year$doy, one_year$std_conductivity,
    type = "l", col = "lightblue", lwd = 2,
    xlab = "day of the year", ylab = "mean daily immersion (0-1)", main = unique(immersion$individ_id)[1]
)
``` 

