### Population maps

#### Prepare workspace & load data
```{r, fake_imm_setup, echo=TRUE, eval = FALSE, message=FALSE}
# Load libraries
library(ncdf4) # For working with netCDF files
library(terra) # For working with rasters


# point R to the folder where the data is, e.g.
data_dir <- "path/where/you/unzipped/files/data"
```

```{r, imm_setup, echo=FALSE, message=FALSE}
# THE ABOVE BLOCK IS FAKE TO SHOW HOW TO SET THE PATH
# Load libraries
library(ncdf4)
library(terra)
```

```{r, generate_popmap_path, echo = FALSE, message = FALSE}
load_chunk <- knitr::knit_expand(text = c(
    "```{r, load_popmap_files}",
    'loaded_netcdf <- nc_open(file.path(data_dir, "{{pop_map_paths[[1]]}}"))',
    "```"))

```

`r knitr::knit(text=load_chunk)`

#### Explore data

The population map netCDF consists of several variables. These are both standard variables and *dimension* variables. 
Standard variables include data about colonies and multidimensional rasters of population estimates. 
The dimensions of these multidimensional rasters correspond to *dimensional* variables. 
This includes latitude and longitude, but the month of the year and which colony these estimates derived from are also dimension variables.
The population estimate variable (and corresponding confidence interval estimates) are therefore four dimensional matrices where each pixel contains population estimates (birds per pixel).

This is a brief tutorial about how to explore and extract data.

Show ALL file metadata. This will list both variables and dimensions. The output is not shown here due to length. 
Note that each variable lists its corresponding dimensions in square brackets, e.g. `PredictedAbundanceMean[lon,lat,month,colonyCode]`

```{r, explore_popmap, eval = FALSE}
print(loaded_netcdf)
```

Net CDF Global attributes correspond to the whole file. This includes the data source, citation and the CRS code of the included rasters. 
Values of these can be obtained using `ncatt_get`
```{r, all att}
ncatt_get(loaded_netcdf, varid = 0)
```

Check CRS code.
```{r, crs}
ncatt_get(loaded_netcdf, varid = 0)$CRS
```

Show colonies in a dataframe by extracting variables by name using `ncvar_get`
```{r, explore_popmap2}
# Define vector variable names we want to extract
varnames <- c("colonyCode", "colonyName", "colonyLatitude", "colonyLongitude", "colonyRegion", "colonyNpairs", "SmcolName")
# For each value of varnames, extract from the netcdf file
variable_list <- lapply(varnames, function(name) {
    ncvar_get(loaded_netcdf, name)
})
#assign varnames as the column names
names(variable_list) <- varnames
#convert to a data frame
colonies <- as.data.frame(variable_list)
#show the first rows
head(colonies)
```

Select a specific colony based on colony name.
```{r, get}
# get the first name in this data
selname <- ncvar_get(loaded_netcdf, "colonyName")[1]
print(selname)
# Get the colony 
colcode <- ncvar_get(loaded_netcdf, "colonyCode")[ncvar_get(loaded_netcdf, "colonyName") == selname]
length(colcode) # See how many sub-colonies correspond to this name
```

In order to work with the population estimates, specific slices must be extracted from the multidimensional matrix. 
These slices will be two dimensional matrices that will be easier to visualise.

To get a single slice first get the data using `ncvar_get` and then index it using standard matrix indexing.
Leave the first two dimensions blank, in order to obtain all values of Latiude and Longitude. 
The last two dimensions should contain a single index corresponding to month and colony.
For example, to get the estimates fro January for the fist colony in these data.
```{r singleslice}
month_colony_slice <- ncvar_get(loaded_netcdf, "PredictedAbundanceMean")[, , 1, 1]
```

To select a colony by name, similar notation to above can be used.

```{r slicebyname, eval = FALSE}
# Boolean of which colony name equals our desired name.
name_bool <- ncvar_get(loaded_netcdf, "colonyName") == selname
# Use this boolean to slice the matrix, taking the first month still.
month_colony_slice <- ncvar_get(loaded_netcdf, "PredictedAbundanceMean")[, , 1, name_bool]
```

Note that depending on the number of subcolonies, this might result in more than one slice (a three dimensional matrix).

#### Plot

Using our single slice of the multidimensional matrix, we can convert it to a raster and make a simple map. 
We will first transpose the matrix as you may have noted that Longitude is on the X axis in the NetCDF, and Latitude on the Y axis.

```{r, getslice, out.width="100%", out.height="600px"}
#transpose the matrix
month_colony_slice_transposed <- t(month_colony_slice)
# convert it to a raster
slice_raster <- rast(month_colony_slice_transposed)
#simple plot
terra::plot(slice_raster, main = paste("January", selname, "Colony code: ",colcode[1]))
```

The Terra spatial raster class supports multiple layers. We can use this to work with a three dimensional raster

Here all 12 months for a single colony are converted to a SpatRaster by leaving the third dimension (month) blank.

```{r, get3dslice, out.width="100%", out.height="800px"}

allmonth_colony_slice <- ncvar_get(loaded_netcdf, "PredictedAbundanceMean")[, , , 1]

# This results in an array (of matrix slices)
# Convert first to raster 

allmonth_colony_raster <- rast(allmonth_colony_slice)
#Transpose it so the map is the right way up
allmonth_colony_raster <- terra::t(allmonth_colony_raster)
# Plot with colony code and month of the year
terra::plot(allmonth_colony_raster, main = paste("Colony code: ",colcode[1], c(1:12)), mar = c (0.5,1,0.5,4))

```

