---
output: 
  html_document:
      toc: true
      toc_depth: 3
      toc_float: true
params:
  request_name: "myrequest2025"
  file_list: !r c("locations.parquet")
  species: !r c("seagull")
  colonies: !r c("big cliff by the sea")
  times: !r as.Date(c("2020-01-01","2020-02-02"))
  data_responsible: !r data.frame()
  creation_date: !r Sys.Date()
  data_dir: ""
  notes: ""
  additional_files: !r list()
title: "`r paste(params$request_name, 'README', params$creation_date)`"
---

```{r, setup , echo = FALSE, message = FALSE, warning = FALSE}
data_dir <- file.path(params$data_dir, "data") # to use in the rest of the examples

md_list <- function(values) {
  if (is.null(values)) {
    return("")
  }
  md_items <- sapply(values, function(value) {
    knitr::knit_expand(text = "| - *{{value}}*")
  })
  return(paste(md_items, collapse = "\n"))
}

render_schema <- function(dataset_key, dict) {
  dataset <- dict$datasets[[dataset_key]]
  title <- gsub("_", " ", tools::toTitleCase(dataset_key))
  header <- knitr::knit_expand(text = "### {{title}} \n\n {{dataset$description}}")

  bullets <- sapply(dataset$columns, function(col) {
    knitr::knit_expand(text = "- **{{col$name}}** *(type: {{col$type}})* \n  {{col$description}} ")
  })
  all_desc <- paste(c(header, bullets), collapse = "\n\n")
  return(all_desc)
}

description_list <- sapply(params$file_list, function(file_item) file_item$description)
description_string <- paste(paste(description_list[1:(length(description_list) - 1)], collapse = ", "), description_list[length(description_list)], sep = " and ")

file_list <- c()

if (length(params$additional_files) > 0) {
  for (additional_file in params$additional_files) {
    filename <- basename(additional_file$path)
    file_list <- c(file_list, '| -- {{additional_file$description}} (<span style="color: #ABB2B9;">{{filename}}</span>)')
  }
}
file_list <- c(file_list, "| -- data")

included_data <- c()
for (i in seq_along(params$file_list)) {
  included_data <- c(included_data, names(params$file_list)[i])
  if ("files" %in% names(params$file_list[[i]])) {
    file_list <- c(file_list, "<details>")
  }

  if ("files" %in% names(params$file_list[[i]])) {
    base_text <- "<summary>&nbsp;"
  } else {
    base_text <- "| &nbsp;&nbsp;&nbsp;&nbsp;"
  }

  base_text <- paste0(base_text, "|-- {{params$file_list[[i]]$description}}")
  if ("path" %in% names(params$file_list[[i]])) {
    base_text <- paste(base_text, '(<span style="color: #ABB2B9;">{{params$file_list[[i]]$path}}</span>)')
  }
  if ("files" %in% names(params$file_list[[i]])) {
    base_text <- paste0(base_text, " - click to expand</summary>")
  }
  file_list <- c(file_list, knitr::knit_expand(text = base_text))


  if ("files" %in% names(params$file_list[[i]])) {
    for (j in seq_along(params$file_list[[i]]$files)) {
      base_text <- "| &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;|-- {{params$file_list[[i]]$files[[j]]$description}}"
      if ("path" %in% names(params$file_list[[i]]$files[[j]])) {
        sub_path <- basename(params$file_list[[i]]$files[[j]]$path)
        base_text <- paste(base_text, '(<span style="color: #ABB2B9;">{{sub_path}}</span>)')
      }
      file_list <- c(file_list, knitr::knit_expand(text = base_text))
    }
    file_list <- c(file_list, "</details>")
  }
}

file_list <- paste(knitr::knit_expand(text = file_list), collapse = "\n")
species_list <- md_list(unique(params$species))
colony_list <- md_list(unique(params$colonies))
time_span <- knitr::knit_expand(text = "| - *{{params$times[1]}}* - *{{params$times[2]}}*")
additional_notes <- knitr::knit_expand(text = "| {{params$notes}}")

has_pop <- any(grepl("Abundance_model", included_data))
has_pos <- "GLS_positional_data" %in% included_data
has_irma_pos <- any(grepl("IRMA_positional_data", included_data))
# To pull the generic overview from the YAML
if (has_pop) {

  included_data <- c(included_data, "population_maps")
}
if (has_irma_pos) {
  included_data <- c(included_data, "IRMA_positional_data")
}

# Load schema
schema_dict <- seatrackR::schema_dict

included_schema <- names(schema_dict$datasets)[names(schema_dict$datasets) %in% included_data]

schema_md <- paste(sapply(included_schema, render_schema, dict = schema_dict), collapse = "\n\n")

image_path <- system.file("img", "SEATRACK_logo_landscape.jpg", package = "seatrackR")
```

```{r include-package-image, echo=FALSE}
knitr::include_graphics(image_path)
```

## Description
| ___________________________________________________________________________________________________
| This readme contains an overview of the files contained within this data package and instructions on how to use them in R. The data package contains `r description_string`.
`r knitr::knit(text = additional_notes)`
|
| *For more information about the project, please visit [SEATRACK's website](https://seatrack.net/)*
| *contact re. General data queries: julian.evans@nina.no & Svenja.Neumann@npolar.no*
| *contact re. For general queries about the contents and creation of this data package: julian.evans@nina.no*
|
`r if(has_pos) {"| *For more information about the processing of GLS data, please see this [report](https://brage.nina.no/nina-xmlui/handle/11250/2735757)*"}`
`r if(has_pos) {"| *contact re. GLS data processing: vegard.brathen@nina.no*"}`
`r if(has_pop) {"| *For more information about the creation of population maps, please see this [paper](https://www.int-res.com/articles/meps_oa/m676p255.pdf)*"}`
`r if(has_pop) {"| *Contact re. Population maps: arnaud.tarroux@nina.no*"}`
`r if(has_irma_pos) {"| *For more information about the use of IRMA to fill in gaps in the GLS data, please see this [report](https://brage.nina.no/nina-xmlui/handle/11250/2595504) and the disclaimer below*"}`
`r if(has_irma_pos) {"| *contact re. IRMA: arnaud.tarroux@nina.no*"}`
| ___________________________________________________________________________________________________
## Package overview
| __________________________________________________________________________________________________
| **The dataset consists of:**
| **Files**:
| -- This readme (<span style="color: #ABB2B9;">`r paste0("README_", params$request_name, "_", params$creation_date, ".html")`</span>)
`r knitr::knit(text = file_list)`
|
| **Time range**
`r knitr::knit(text = time_span)`
|
| **Species**: 
`r knitr::knit(text = species_list)`
| 
| **Colonies**: 
`r knitr::knit(text = colony_list)`
|
| **Data responsible**:
`r knitr::kable(params$data_responsible, col.names = c("Species", "Colony", "Responsible persons"))`
| ___________________________________________________________________________________________________
## Data use disclaimer
| ___________________________________________________________________________________________________
| Data is shared under the [Agreement of Understanding](https://seatrack.net/wp-content/uploads/2024/11/SEATRACK_Agreement-of-understanding_2024.pdf).
| Depending on the intended use of the data, include the SEATRACK program group and data responsible individuals early in the process. 
| Follow the guidelines in the [Agreement of Understanding](https://seatrack.net/wp-content/uploads/2024/11/SEATRACK_Agreement-of-understanding_2024.pdf).
| ___________________________________________________________________________________________________
## Examples of use

```{r, show_examples, echo=FALSE, results='asis'}
if (has_pos) {
  pos_path <- [[which(grepl("GLS_positional_data", names(params$file_list)))[1]]]
  res <- knitr::knit_child(system.file("Rmd", "EXAMPLES_locations.Rmd", package = "seatrackRtools"),
    quiet = TRUE, envir = environment()
  )
  cat(res, sep = "\n")
}

if (has_irma_pos) {
  IRMA_pos_path <- params$file_list[[which(grepl("IRMA_positional_data", names(params$file_list)))[1]]]$path
  res <- knitr::knit_child(system.file("Rmd", "EXAMPLES_IRMA_locations.Rmd", package = "seatrackRtools"),
    quiet = TRUE, envir = environment()
  )
  cat(res, sep = "\n")
}

if ("individual_data" %in% included_data) {
  indiv_path <- params$file_list[[which(grepl("individual_data", names(params$file_list)))[1]]]$path
  res <- knitr::knit_child(system.file("Rmd", "EXAMPLES_individuals.Rmd", package = "seatrackRtools"),
    quiet = TRUE, envir = environment()
  )
  cat(res, sep = "\n")
}

if ("light_data" %in% included_data) {
  light_path <- params$file_list[[[[which(grepl("light_data", names(params$file_list)))[1]]]]]$path
  res <- knitr::knit_child(system.file("Rmd", "EXAMPLES_light.Rmd", package = "seatrackRtools"),
    quiet = TRUE, envir = environment()
  )
  cat(res, sep = "\n")
}

if ("immersion_data" %in% included_data) {
  imm_path <- [[which(grepl("immersion_data", names(params$file_list)))[1]]]
  res <- knitr::knit_child(system.file("Rmd", "EXAMPLES_immersion.Rmd", package = "seatrackRtools"),
    quiet = TRUE, envir = environment()
  )
  cat(res, sep = "\n")
}

if (has_pop) {
  pop_map_paths <- sapply(params$file_list[grepl("Abundance_model", names(params$file_list))], function(x) {
    x$path
  })
  res <- knitr::knit_child(system.file("Rmd", "EXAMPLES_popmap.Rmd", package = "seatrackRtools"),
    quiet = TRUE, envir = environment()
  )
  cat(res, sep = "\n")
}
```

## Detailed file description

`r knitr::knit(text = schema_md)`

